Mahotas: Open source software for scriptable computer vision

### 2012-08-28 paper.tex
ENH Add information fields

@@

\section{Functionality and Interface}

@@

\begin{description}
\item[\textsc{surf}] Speeded-up Robust Features~\citep{eth_biwi_00517}. This is
a collection of local features.
\item[features] Global feature descriptors. In particular, Haralick texture
features, Zernike moments, local binary patterns, threshold adjacency
statistics.
\item[Wavelet] Haar and Daubechies wavelets. Forward and reverse transforms.
\item[morphological functions] Erosion and dilation, as well as some more
complex operations built on these. There are both binary and grayscale
implementations of these operators.
\item[watershed] seeded watershed and distance map
transforms~\citep{felzenszwalb}.
\item[filtering] Gaussian filtering and general convolutions.
\item[polygon operations] convex hull, polygon drawing.
\end{description}

@@

\section{Implementation}

@@

@@

>>>>

\textbf{Keywords:} computer vision, image processing.

@@

\section{Implementation and Architecture}

\subsection{Interface}

@@

\begin{description}
\item[\textsc{surf}] Speeded-up Robust Features~\citep{eth_biwi_00517}. This is
a collection of local features.
\item[features] Global feature descriptors. In particular, Haralick texture
features, Zernike moments, local binary patterns, threshold adjacency
statistics.
\item[Wavelet] Haar and Daubechies wavelets. Forward and inverse transforms.
\item[morphological functions] Erosion and dilation, as well as some more
complex operations built on these. There are both binary and grayscale
implementations of these operators.
\item[watershed] seeded watershed and distance map
transforms~\citep{felzenszwalb}.
\item[filtering] Gaussian filtering and general convolutions.
\item[polygon operations] convex hull, polygon drawing.
\end{description}

@@

\subsection{Implementation}

@@

\subsection{Quality Control}

Mahotas includes a complete automated suite of unit tests. These all
functionality and include several regression tests. There are no known bugs in
version~1.0. In fact, no releases have ever been performed with known bugs.
Naturally, bugs were, occasionally, discovered in released versions, but
corrected before the next release.

The development is completely open-source and development versions are
available. Many users have submitted bug reports and fixes.

\section{Availability}

\textbf{Operating system}\\
Mahotas runs and is used on different versions of Unix (including Linux, SunOS,
and FreeBSD), Mac OS X, and Windows.

\textbf{Programming language}\\
Mahotas works in Python (minimal version is~2.5 and works in all more recent
versions, including in the Python~3 series).

\textbf{Additional system requirements}\\
None.

\textbf{Dependencies}\\
It requires numpy to be present and installed.

\textbf{List of contributors}\\
Luis Pedro Coelho, Zachary Pincus, Peter J. Verveer, Davis King, Robert Webb
(Carnegie Mellon University), Matthew Goodman, K.-Michael Aye (University of
Bern), Rita Simões, Joe Kington (University of Wisconsin Dept. of Geoscience),
Christoph Gohlke (University of California, Irvine), and Sandro Knauss.

\subsubsection{Software location}

\textbf{Code repository}\\
\textit{Name}: Github\\
\textit{Identifier}: https://github.com/luispedro/mahotas\\
\textit{Licence}: MIT\\
\textit{Date published}: Since 2009

@@

\section{Reuse Potential}

Originally, this code was developed in the context of cellular image analysis.
However, none of the functionality is specific to this context and many
computer vision pipelines can make use of it.
